\documentclass[11pt]{article}
\input{header}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\usetikzlibrary{shapes.multipart}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{intersections, pgfplots.fillbetween}

\setlength{\textheight}{11.00in}
\setlength{\topmargin}{-0.2in}

\title{
\vspace{-1.2cm}
Data Science 2021-22\\ Final Exam}
\author{13 December 2021}
\date{}%Name: \dotfill}% NIA: \dotfill}

\newcounter{marks}
\setcounter{marks}{0}

\def\ci{\perp\!\!\!\perp}

\begin{document}

\maketitle

\newcounter{PreguntaCounter}

\section*{Hypothesis testing}
\begin{list}{{\bf Question 1.\arabic{PreguntaCounter}:}}
	{\usecounter{PreguntaCounter}
	}

\item
\fbox{1 points}
\addtocounter{marks}{1}
In order to evaluate the effect of a drug over a disease a pharmaceutical company wants to perform a study comparing the effect of the drug with placebo. The drug and the placebo will be delivered to both male and female patients. The effect of the drug will be measured in 10th of reduction of any of the 5 possible symptoms of the disease. How many factors and dependent variables this analysis has? Which are they?

\item
\fbox{1 points}
\addtocounter{marks}{1}
In the previous question, should the threshold for the test of each dependent variable be 5%? Explain your answer.

\item
\fbox{1 points}
\addtocounter{marks}{1}
In a hospital a research is carried out with the aim to identify the best rehabilitation technique after knee surgery. The doctors want to compare three different devices against a standard expert physiotherapist. The efficacy of the rehabilitation is estimated by the measurement of the degrees of flexion of the knee. Which series of test would you suggest to the medical team? Explain your answer.

\end{list}

\pagebreak

%Name: \dotfill

\section*{Unsupervised learning}
\begin{list}{{\bf Question 2.\arabic{PreguntaCounter}:}}
	{\usecounter{PreguntaCounter}
	}

\item
\fbox{1 point}
\addtocounter{marks}{1}
We have a 2D dataset and we want to reduce its dimensionality to 1D using PCA. The first principal axis is given by eigenvector $(0.6940, 0.7200)^T$. a) What is the PCA representation for the data sample $(5.51,5.35)$ in the first principal axis? b) Consider the 1D representation of that data sample according to PCA. Which are the coordinates (in the original space) of the reconstructed sample? c) Which is the reconstruction error if you  would use two principal components?   

\item
\fbox{0.5 point}
\addtocounter{marks}{1}
What is manifold learning? Give an example of a linear manifold learning method and another of nonlinear manifold learning method 

\item
\fbox{0.5 point}
\addtocounter{marks}{1}
What are the caveats when clustering using the k-means algorithm? Mention at least two of them, together with possible solutions/alternatives methods to avoid them or minimize their impact.
\end{list}

\section*{Supervised learning}
\begin{list}{{\bf Question 3.\arabic{PreguntaCounter}:}}
	{\usecounter{PreguntaCounter}
	}

\item
\fbox{1 point}
\addtocounter{marks}{1}
A company develops an application that estimates how long it takes for users to drive to work. To do so, the company collects data of users driving to work, recording the initial and final location of the drive, and the time of day at the beginning and at the end. Formalize this as a supervised learning problem. Which are the concrete components of this learning problem?

\item
\fbox{1 point}
\addtocounter{marks}{1}
What is the difference between empirical risk and true risk? Using the concepts of empirical risk and true risk, explain what overfitting means.

\end{list}

\section*{Deep learning}
\begin{list}{{\bf Question 4.\arabic{PreguntaCounter}:}}
	{\usecounter{PreguntaCounter}
	}

\item
\fbox{1 point}
\addtocounter{marks}{1}
How are recurrent neural networks (RNNs) different from feedforward neural networks (FNNs)? Describe an application in which RNNs would be more appropriate than FNNs.

\item
\fbox{1 point}
\addtocounter{marks}{1}
In a convolutional neural network, explain how a convolutional layer is structured. How is a convolutional layer different from a fully connected layer?

\item
\fbox{1 point}
\addtocounter{marks}{1}
List 3 different ways in which we can alleviate the problem of overfitting in deep learning.

\item
\fbox{1 point}
\addtocounter{marks}{1}
In the context of deep learning, explain how a softmax layer works and provide its formula.

\end{list}

\end{document}
